---
title: 'Weekly Exercises #6'
author: "Yunyang Zhong"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)     # for data cleaning and plotting
library(gardenR)       # for Lisa's garden data
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(palmerpenguins)# for Palmer penguin data
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(gifski)        # for creating the gif (don't need to load this library every time,but need it installed)
library(transformr)    # for "tweening" (gganimate)
library(shiny)         # for creating interactive apps
library(patchwork)     # for nicely combining ggplot2 graphs  
library(gt)            # for creating nice tables
library(rvest)         # for scraping data
library(robotstxt)     # for checking if you can scrape data
theme_set(theme_minimal())
```

```{r data}
# Lisa's garden data
data("garden_harvest")

#COVID-19 data from the New York Times
covid19 <- read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv")

```

## Your first `shiny` app 

  1. This app will also use the COVID data. Make sure you load that data and all the libraries you need in the `app.R` file you create. Below, you will post a link to the app that you publish on shinyapps.io. You will create an app to compare states' cumulative number of COVID cases over time. The x-axis will be number of days since 20+ cases and the y-axis will be cumulative cases on the log scale (`scale_y_log10()`). We use number of days since 20+ cases on the x-axis so we can make better comparisons of the curve trajectories. You will have an input box where the user can choose which states to compare (`selectInput()`) and have a submit button to click once the user has chosen all states they're interested in comparing. The graph should display a different line for each state, with labels either on the graph or in a legend. Color can be used if needed. 

> [shiny](http://127.0.0.1:6387/)
  
## Warm-up exercises from tutorial

  2. Read in the fake garden harvest data. Find the data [here](https://github.com/llendway/scraping_etc/blob/main/2020_harvest.csv) and click on the `Raw` button to get a direct link to the data. 

```{r}
library(readr)
X2020_harvest <- read_csv("https://raw.githubusercontent.com/llendway/scraping_etc/main/2020_harvest.csv", 
    col_types = cols(weight = col_double()),
    na = "MISSING", 
    skip = 2) %>% 
  select(-X1)

X2020_harvest
```
  
  3. Read in this [data](https://www.kaggle.com/heeraldedhia/groceries-dataset) from the kaggle website. You will need to download the data first. Save it to your project/repo folder. Do some quick checks of the data to assure it has been read in appropriately.

```{r}
Groceries_dataset <- read_csv("Groceries_dataset.csv", 
    col_types = cols(Member_number = col_character()))

Groceries_dataset
```

  4. CHALLENGE(not graded): Write code to replicate the table shown below (open the .html file to see it) created from the `garden_harvest` data as best as you can. When you get to coloring the cells, I used the following line of code for the `colors` argument:
  
```{r}
garden_harvest %>% 
  filter(vegetable %in% c("beans", "carrots", "tomatoes")) %>% 
  mutate(month = month(date, label = TRUE),
         vegetable = ifelse(vegetable == "beans", "Beans", ifelse(vegetable == "carrots", "Carrots", "Tomatoes")),
         variety = ifelse(variety == "greens", "Greens", ifelse(variety == "grape", "Grape", ifelse(variety == "volunteers", "Volunteers", variety)))) %>% 
  group_by(vegetable, variety, month) %>% 
  mutate(total_wt_lb = sum(weight * 0.00220462)) %>% 
  select(-date, -weight, -units) %>% 
  distinct(variety, .keep_all = TRUE) %>% 
  arrange(vegetable, variety) %>% 
  pivot_wider(id_cols = vegetable:variety,
              names_from = month,
              values_from = total_wt_lb) %>% 
  group_by(vegetable) %>% 
  gt() %>% 
  cols_label(
    variety = ""
  ) %>% 
  tab_header(
    title = md("Bean, Carrot, and Tomato Harvest (lb)")) %>% 
  tab_footnote(
    footnote = "Month is not complete yet",
    locations = cells_column_labels(columns = Oct)
  ) %>% 
  fmt_number(
    columns = c(Jul, Aug, Sep, Oct),
    decimals = 2) %>%
  fmt_missing(
    columns = c(Jul, Aug, Sep, Oct),
    missing_text = 0) %>% 
  summary_rows(columns = c(Jul, Aug, Sep, Oct),
               groups = TRUE,
               fns = list(sum = ~sum(.,na.rm = TRUE))) %>% 
  data_color(columns = c(Jul, Aug, Sep, Oct),
             colors = scales::col_numeric(
      palette = paletteer::paletteer_d(
        palette = "RColorBrewer::YlGn"
      ) %>% as.character(), domain = NULL))
```

  5. Create a table using `gt` with data from your project or from the `garden_harvest` data if your project data aren't ready.
  
  6. Use `patchwork` operators and functions to combine at least two graphs using your project data or `garden_harvest` data if your project data aren't read.
  
> [github](https://github.com/yzhong0620/STAT-112-Weekly-Exercises-6/blob/master/06_exercises.md)

**DID YOU REMEMBER TO UNCOMMENT THE OPTIONS AT THE TOP?**